### 2014-06-06 evaluation.tex
Removed time 0 ms from table
evaluation figures and some text

\section{Evaluation}\label{evaluation}

(All results are on PASCAL VOC 2007 and 2010. ILSVRC is nice-to-have.)

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  {[}TABLE: Dense region evaluation, timing vs.~accuracy: effect of
  multi scale, pooling.{]}
\item
  From the above, we select the point of high accuracy and reasonable
  cost.
\item
  {[}PLOT: Cascaded CNN timing vs.~accuracy: effect of threshold.{]}
\item
  From the above, we select threshold of high accuracy and reasonable
  cost.
\item
  {[}TABLE: Combined system timing vs accuracy: effect of dynamic region
  selection.{]}
\end{itemize}

>>>>

%!TEX root=paper.tex
\section{Evaluation}\label{sec:evaluation}

We evaluate on the standard object detection benchmark: the PASCAL VOC \todo{cite?}.
In all cases, the CNN region classifiers are trained on the PASCAL VOC 2007 trainval set.
The parameters of our methods are set by training or cross-validation on the VOC 2007 val set.
We evaluate on the VOC 2007 test set.

The R-CNN software was used as available in June 2014\footnote{\url{https://github.com/rbgirshick/rcnn}}.
That software relies on Selective Search \cite{Uijlings-IJCV-2013} region proposals.
Different images are proposed different numbers of regions.
\autoref{fig:roi_hist} shows the distribution of number of regions on the validation set, with the parameters of the R-CNN.

An additional parameter is the size of each batch of regions that goes through the CNN.
We set batch size to 100 regions, and observe that it takes on average 500 ms to process them with the CNN.
In all experiments, we use Ubuntu 12.04, Intel i5 3.2GHz CPU, and NVIDIA Tesla K40 GPU.

\autoref{fig:voc2007_results} and \autoref{tab:results} show the results.

\begin{figure}[ht]
\centering
\begin{subfigure}[b]{0.52\linewidth}
    \includegraphics[width=\linewidth]{figures/_apvst_final.pdf}
    \caption{mAP vs. time allotted for detection}\label{fig:apvst}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{figures/_speedup_final_abs.pdf}
    \caption{mAP vs. speed-up factor}\label{fig:speedup}
\end{subfigure}
\caption{
Results on the PASCAL VOC 2007 dataset.
(a) On the left-hand mAP vs. Time plot, we can compare APs at a given allotted time point.
For example, at 1300 ms, random region selection gets about 0.42 mAP, while our best method (C-CNN with gradient-based region selection) obtains 0.50 mAP.
(b) On the right-hand speed-up plot, we can compare speed-ups at a given mAP point.
For example, we can see that we should obtain mAP of 0.40 at around 20x speedup with our method.
}\label{fig:voc2007_results}
\end{figure}

\begin{table}[ht]
\centering
\caption{
Full table of AP vs. Time results on PASCAL VOC 2007.
}\label{tab:results}
\small{
\include{results_table}
}
\end{table}

\begin{description}
  \item[Original] \hfill \\
  The original order of the
  \item[Second] \hfill \\
  The second item
  \item[Third] \hfill \\
  The third etc \ldots
\end{description}

\begin{figure}
\centering
\begin{subfigure}[b]{0.52\linewidth}
    \includegraphics[width=\linewidth]{figures/roi_hist.pdf}
    \caption{Distribution of number of regions per image.}\label{fig:roi_hist}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.46\linewidth}
    % \includegraphics[width=\linewidth]{PLACEHOLDER}
    \rule{5cm}{4cm}
    \caption{\todo{Another small figure here}}\label{fig:PLACEHOLDER}
\end{subfigure}
\caption{}
\end{figure}

### 2014-06-06 method.tex
done with abstract
evaluation figures and some text

Our method builds on the architecture described in \cite{Girshick-CVPR-2014}.
As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs), and then does the following: (1) for each ROI, classifies it with a CNN, obtaining multi-class scores; (2) post-processes the scored ROIs with non-maximal suppression and other bounding box refinement to obtain the final detections.

We aim to incorporate several speed-ups into a similar architecture.
As summarized in \autoref{fig:combined}, we start with the same ROI proposals, and then (1) score each proposal with a quick-to-compute feature; (2) select the ROI that is most promising, and score it with a CNN, which is additionally sped up with a cascaded structure; (3a) either select another ROI, incorporating the scores of the first one into the selection -- or (3b) post-process the ROIs scored so far and exit.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\linewidth]{figures/roi_hist.pdf}
\caption{
    Distribution of the number regions per image on PASCAL VOC2007 validation set.
}\label{fig:roi_hist}
\end{figure}

\begin{table}[ht]
\centering
\caption{
Full table of AP vs. Time results on PASCAL VOC 2007.
}\label{tab:results}
\include{results_table}
\end{table}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\linewidth]{figures/_speedup.pdf}
\caption{
Speedup.
}\label{fig:speedup}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\linewidth]{figures/_all_selected.pdf}
\caption{
AP vs. Time plots.
}\label{fig:apvst}
\end{figure}

>>>>

We take the Region-CNN (R-CNN) \cite{Girshick-CVPR-2014} method as our point of departure.
As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs), and for each batch of ROIs, transforms them to canonical size and classifies with a CNN, obtaining multi-class scores.
After all batches have scores, ROIs are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.

As summarized in \autoref{fig:combined}, we start with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
We then select a batch of highly-scoring ROIs and classify them with the CNN -- but the CNN may additionally be sped up with cascaded structure.
After the batch is scored, we optionally re-score the remaining ROIs, and repeat.

@@
